MaxEnt: What is it good for?

### 2015-06-19 ms.tex
Some writing and reordering

@@

\section{What is testable information?}

@@

\section{A special case: expected values}\label{sec:expectations}
The most common kind of testable information analysed using MaxEnt is
expected values. Updating from a prior $\boldsymbol{q}$ to a posterior
$\boldsymbol{p}$ given an expected value constraint:

@@

\section{MaxEnt and Bayesian inference}\label{sec:bayes}

\section{MaxEnt and ``Hierarchical Bayesian'' models}
Suppose we have a discrete prior distribution $q(\xx)$. Consider some
function of the unknown quantity, $f(\xx)$.
If the value of $f(\xx)$ is known, then our distribution for $\xx$ can
be updated from $q$ to $p$ as in Section~\ref{sec:bayes}.
If we receive testable information
about the expected value of $F$, then our distribution for $\xx$ can
be updated as in Section~\ref{sec:expectations}.

>>>>

Throughout this article I will present, but not derive or prove, MaxEnt
results for certain types of testable information.

@@

\section{What is testable information?}
{\it Testable information} refers to information given in the form of
{\it a constraint that our probability distribution should satisfy}. This is
different from the kind of information we normally use in Bayesian inference,
which is the truth of a proposition. An example of testable information
might be $P(x > 7) = 0.4$. That is, our probability distribution should have
the property that there's a 40\% probability of $x$ being greater than 7.
If our current (prior) probability distribution $q$ already has this property,
then we needn't do anything. However, if $q$ does not satisfy this property,
we use MaxEnt to choose a new distribution, the posterior $p$.

The posterior $p$ will satisfy the constraint given in the testable information,
and will be as close to $q$ as possible while doing so.

\section{Special case 1: expected values}\label{sec:expectations}
The most common kind of testable information analysed using MaxEnt is
expected values. Updating from a prior $\boldsymbol{q}$ to a posterior
$\boldsymbol{p}$ given an expected value constraint:

@@

\section{MaxEnt with constraints on conditionals: the ``entropic prior''}

\section{MaxEnt with constraints on marginals: ``hierarchical Bayes''}
Suppose we have a discrete prior distribution $q(\xx)$. Consider some
function of the unknown quantity, $f(\xx)$.
If the value of $f(\xx)$ is known, then our distribution for $\xx$ can
be updated from $q$ to $p$ as in Section~\ref{sec:bayes}.
If we receive testable information
about the expected value of $F$, then our distribution for $\xx$ can
be updated as in Section~\ref{sec:expectations}.

@@
